Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-09 main.tex
Reorganize references

\usepackage[utf8]{inputenc}
\usepackage{ebproof}
\usepackage{amsmath}
\usepackage{ebproof}
\usepackage{virginialake}
\usepackage{cmll}
\usepackage{tikz}
\usepackage{natbib}
\usepackage{amsthm}\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Combinatorial Proofs and Decomposition Theorems for First-order Logic}

@@

We consider Gentzen's sequent calculus system $\LK$ \cite{Gentzen 1935}.

@@

In this paper, we also use some \bfit{deep inference} \cite{BT 2001} rules that are in the
following form:
\begin{center}
\begin{prooftree}
  \hypo{\vdash S\{A\}}
  \infer1[]{\vdash S\{B\}}
\end{prooftree}
\end{center}
where $S\{ \ \}$ stands for a \bfit{context}, which corresponds to a sequent
with a hole taking the place of an atom, and $S\{A\}$ represents
the sequent or formula obtained by replacing the hole in $S\{ \ \}$ with the formula $A$. Formally, 
\begin{center}
  $C ::= \Box \ | \ A \cor C \ | \ C \cand A \ | \ \exists x C \ | \ \forall x 
C$.
\\[1.5ex]
  $S ::= C \ | \ A, S \ | \ S, A$ 
\end{center}
where $A$ is a formula.
The above rule can be thus seen as the rewriting rule $A \rightarrow B$.

@@

\subsection{Decomposition Theorem}
Consider the following deep inference rules \cite{BT 2001}:
\begin{center}
\mbox{
\begin{prooftree}
  \hypo{\vdash S\{A \cor A\}}
  \infer1[$\cD$]{\vdash S\{A\}}
\end{prooftree}
\hspace{2cm}

@@

D. Hughes proves in \cite{Hughes 2019} the soundness and completeness of
unification nets with respect to $\FOMLLm$. In the following, we establish the
equivalence between unification nets and fonets.

@@

\begin{proposition}
If one of the switching graphs of the unification structure of $A$
contains a cycle or is not connected, then there exists an induced bimatching of the
corresponding linked fograph.
\begin{proof}
We use frames introduced by D. Hughes in Section 4 of \cite{Hughes 2015}.

@@

If $H$ contains a cycle, then the corresponding switching graph of $\theta_m$ also contains a cycle. Hence, by applying the propositional results (Theorem 7) from \cite{Retore 2003}, we conclude that there exists a chordless, alternating, and elementary cycle in the bicoloured graph ($W, E_W \uplus L_W$), which corresponds to an induced bimatching in the linked fograph. (Note that the linked fograph (cograph) corresponding to $\theta_m$ is equivalent to the one corresponding to $\theta$.)

@@

By considering propositional encodings, the maps defined are label-preserving skew fibrations on the underlying fographs according to \cite{Strassburger 2007}.

@@

  Therefore, all of these maps are skew bifibrations and since skew bifibrations
on fographs compose (Lemma 10.32, \cite{Hughes 2019}), there exists a skew
bifibration from $\Gr(A)$ to $\Gr(B)$.

@@

\input{bibliography}

>>>>

\usepackage[utf8]{inputenc}
\usepackage{ebproof}
\usepackage{amsmath}
\usepackage{ebproof}
\usepackage{virginialake}
\usepackage{cmll}
\usepackage{tikz}
\usepackage{amsthm}\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]

@@

\begin{document}
\bstctlcite{refs:BSTcontrol}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Combinatorial Proofs and Decomposition Theorems for First-order Logic}

@@

We consider Gentzen's sequent calculus system $\LK$ \cite{gentzen:35:I}.

@@

In this paper, we also use some \bfit{deep inference} \cite{brunnler:tiu:01} rules that are in the
following form:
\begin{center}
\begin{prooftree}
  \hypo{\vdash S\{A\}}
  \infer1[]{\vdash S\{B\}}
\end{prooftree}
\end{center}
where $S\{ \ \}$ stands for a \bfit{context}, which corresponds to a sequent
with a hole taking the place of an atom, and $S\{A\}$ represents
the sequent or formula obtained by replacing the hole in $S\{ \ \}$ with the formula $A$. Formally, 
\begin{center}
  $C ::= \Box \ | \ A \cor C \ | \ C \cand A \ | \ \exists x C \ | \ \forall x 
C$.
\\[1.5ex]
  $S ::= C \ | \ A, S \ | \ S, A$ 
\end{center}
where $A$ is a formula.
The above rule can be thus seen as the rewriting rule $A \rightarrow B$.

@@

\subsection{Decomposition Theorem}
Consider the following deep inference rules \cite{brunnler:tiu:01}:
\begin{center}
\mbox{
\begin{prooftree}
  \hypo{\vdash S\{A \cor A\}}
  \infer1[$\cD$]{\vdash S\{A\}}
\end{prooftree}
\hspace{2cm}

@@

D. Hughes proves in \cite{hughes:unifn} the soundness and completeness of
unification nets with respect to $\FOMLLm$. In the following, we establish the
equivalence between unification nets and fonets.

@@

\begin{proposition}
If one of the switching graphs of the unification structure of $A$
contains a cycle or is not connected, then there exists an induced bimatching of the
corresponding linked fograph.
\begin{proof}
We use frames introduced by D. Hughes in Section 4 of \cite{hughes:unifn}.

@@

If $H$ contains a cycle, then the corresponding switching graph of $\theta_m$
also contains a cycle. Hence, by applying the propositional results (Theorem 7)
from \cite{retore:03}, we conclude that there exists a chordless, alternating, and elementary cycle in the bicoloured graph ($W, E_W \uplus L_W$), which corresponds to an induced bimatching in the linked fograph. (Note that the linked fograph (cograph) corresponding to $\theta_m$ is equivalent to the one corresponding to $\theta$.)

@@

By considering propositional encodings, the maps defined are label-preserving
skew fibrations on the underlying fographs according to
\cite{str:07:RTA}.

@@

  Therefore, all of these maps are skew bifibrations and since skew bifibrations
on fographs compose (Lemma 10.32, \cite{hughes:fopws}), there exists a skew
bifibration from $\Gr(A)$ to $\Gr(B)$.

@@

\bibliographystyle{IEEEtran}
\bibliography{refs}
